
\subsection{Task scheduling}
Consider a cloud service that offers distributed infrastructure to process
jobs, or a modern data processing system that processes queries on large
databases.
In such systems, queries may be passed to an execution planner
which uses statistics, current workloads, and cost models to choose an optimal
plan among a set of candidate execution plans.
These plans are in the form of directed acyclic graphs with edges indicating
task dependencies.
Some metrics for choosing plans include makespan (time to finish executing
the DAG) and resource consumption (e.g., to obtain fairness between queries).
One challenge, however, is that available resources change with time,
so an execution plan deemed optimal before execution can become sub-optimal
during its lifetime~\cite{mahajan2018qoop}.

With this as setting, one may consider learning a decision rule for
scheduling tasks, say for minimizing makespan. We make the simplification
that execution of proceed in rounds (e.g., MapReduce), and suppose that
there is a cost vector $(c_1, \ldots, c_n)$ for scheduling tasks, where
each $c_i$ is the cost of entering round $i$. The objective,
then, is to pack the tasks into as few rounds as possible, while respecting
edge dependencies as much as possible. 

Formally, let $\X$ be some set of feature vectors
(extracted from the query, tasks, resources at time of execution,
time-of-day, and so on), and let
\begin{align*}
  \Y_n &= \{ (G, \vec{c})
  \mid \text{$G$ is a weighted DAG on $[n]$
    and $\vec{c} =( c_n, \ldots, c_n), c_1 < ...< c_n$}
  \}
\end{align*}
Samples $S = \{((x_{i,j})_{j=1}^{n_i}, (G_i, \vec{c}_i))_{i=1}^m\}$ may come from
computing the best DAG in hindsight and collecting statistics. We want the
learning algorithm to output a function that stratifies tasks into rounds,
i.e.,
\begin{align*}
  \Yh = \bigcup_{n=1}^\infty \Yh_n
  = \bigcup_{n=1}^\infty \{f: \bigcup_{i=1}^n \X^n \to \mathbb{Z}_+^n\}.
\end{align*}
We interpret a graph $G$ as just its set of weights $\{y_{i,j}\}_{i,j \in V(G)}$,
and think of $y_{ij} > 0$ to mean that we prefer task $i$ to be scheduled before
task $j$ (moreover with weight $y_{ij}$).

The loss we consider is then
\begin{align*}
  \ell(\vec{y},\vec{c}), f)
  =\sum_{i,j: i \neq j} y_{ij} \1_{\{f(i) \geq f(j)\}}+\sum_{i=1}^r c_i \1[\max_k f(k) \geq i]
\end{align*}
For the first summand, having $f(i) \geq f(j)$ means to schedule $i$ in the
same round as $j$ or after $j$, so we incur a penalty of $y_{ij}^G$ when
this is the case. For the second summand, we sum up the costs of all rounds
that we enter for the schedule. 

It is easy to see that this problem is related to ranking: a scheduling
function $f$ is similar to a scoring function that outputs relevance scores.

 

\input{job-scheduling-mingyang}






